\clearpage
\ifodd\thepage\hbox{}\newpage\else\fi%si page paire ou impaire
\parindent=0pt

\newgeometry{left=2cm,right=3cm}
\restoregeometry

\thispagestyle{empty}

%
\begin{center}
{\Large \textbf{Abstract}}
\end{center}



This report focuses on my work for the duration of my internship. This content is divided into four areas.
The first part provides information on the firm in which I worked and the following three parts describe each of my assignments.
The common point of all is the Java development but for different purposes.




The first assignment was Java test development based on an internal Framework.
It was a very interesting part because of the wealth of expertise and experience found in the project which I integrated.
During this period I accumulated a large amount of knowledge, concerning the Framework itself or the Java.

The second assignment was complement an existing Java class to adapt its behavior to a new used tool.
It was a hard part due to the fact there are many studies to be done for relatively little Java code.
I had to integrate my Java implementation into an already existing code and I was very formative.

The third assignment, and also the most interesting and formative, was the Jenkins plug-in development.
I studied Jenkins and the way to develop a plug-in for a long time. Next, I had to gradually had new features for the purpose of obtain the expected plugin.
The other thing was the human side and the teamwork. Indeed I reported weekly the project progresses and work in pair.



My employer was SAP France, firstly I worked in Levallois-Perret, next to Paris, from July to mid-February. Next, SAP moved towards to a larger building, still in the same town. I worked there until end of September.


It was with a great pleasure to spent my time in there. I learned many things during this internship period, I was able to use new technologies and unknown tools. 


\vspace*{\stretch{2}}

\hrulefill
\begin{center}
{\Large \textbf{Keywords}}
\end{center}
\hrulefill





\begin{center}
Software tester\\
JavaEE\\
Agile\\
Jenkins\\
Plugin\\
\end{center}
